Discon analysis

### 2018-08-30 analysis/01_analysis.Rmd
collect ip

files <- dir("../../pilot_1_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../pilot_1_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))

>>>>

files <- dir("../../adult_relative_raw_data/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_relative_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
